[Artifact Presentation] Damegender: \\ Writing and Comparing Gender Detection Tools

### 2020-05-15 paper2sattose.tex
paper2sattose.tex: fix datasets in features experiment

We have developed some experimental functionality that allows to analyze our database according to some features using machine learning algorithms.
To test our approach, we have selected some features of the names, such as a being the first letter, a (or o) being the last letter, contains the letter a, first letter is a vocal, last letter is a vocal, last letter is a consonant, or last letter is a. 
The selection of the features was verified with Principal Component Analysis.
The datasets used in this experiment were the ones from the Spain National Institute of Statistics and the Natural Language
ToolKit corpus of (English) names.
The most relevant results for the different datasets used are offered in Table~\ref{table:InfoFeatures}.

>>>>

We have developed some experimental functionality that allows to analyze our database according to some features using machine learning algorithms.
To test our approach, we have selected some features of the names, such as a being the first letter, a (or o) being the last letter, contains the letter a, first letter is a vocal, last letter is a vocal, last letter is a consonant, or last letter is a. 
The selection of the features was verified with Principal Component Analysis.
The datasets used in this experiment were the ones from the National Institute of Statistics (Spain, Uruguay, United Kingdom, United States of America, Australia and Canada).
The most relevant results for the different datasets used are offered in Table~\ref{table:InfoFeatures}.
